\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-01-20 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
more logos

The cover graphic of the manual was created by Santiago Lombeyda from
Caltech's Center for Advanced Computing Research (CACR) \urlwithparentheses{http://www.cacr.caltech.edu}.
\\

\section*{Current and past main participants or main sponsors}

\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=0.125\textwidth]{figures/logo_cnrs}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_princeton}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_aix_marseille_universite}\vspace*{0.02truemm}
\includegraphics[width=0.12\textwidth]{figures/logo_CSC_China}\vspace*{0.02truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_ETH}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_inria}\vspace*{2truemm}
\includegraphics[width=0.14\textwidth]{figures/logo_UPPA}
\par\end{centering}

\noindent \begin{centering}
\includegraphics[width=0.15\textwidth]{figures/logo_NVIDIA}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_IUF}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Caltech}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Harvard}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_IPGP}\vspace*{2truemm}
\par\end{centering}

\noindent \begin{centering}
\includegraphics[width=0.119\textwidth]{figures/logo_INGV}\vspace*{2truemm}
\includegraphics[width=0.119\textwidth]{figures/logo_University_of_Toronto}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_TOTAL}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Fairbanks}
\hspace*{3mm}\includegraphics[width=0.130\textwidth]{figures/logo_fondation_Del_Duca}
\par\end{centering}
\end{figure}

>>>>

The cover graphic of the manual was created by Santiago Lombeyda from
Caltech's Center for Advanced Computing Research (CACR) \urlwithparentheses{http://www.cacr.caltech.edu}.\\

The code is released open-source under the GNU version 2+ license, see the license at the end of this manual.\\

\newpage{}
\section*{Current and past main participants or main sponsors (in no particular order)}
%
\begin{figure}[htbp]
\noindent \begin{centering}
\includegraphics[width=0.125\textwidth]{figures/logo_cnrs}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_princeton}\vspace*{2truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_aix_marseille_universite}\vspace*{0.02truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_ETH}\vspace*{2truemm}
\includegraphics[width=0.12\textwidth]{figures/logo_CSC_China}\vspace*{0.02truemm}
\includegraphics[width=0.15\textwidth]{figures/logo_inria}\vspace*{2truemm}
\includegraphics[width=0.14\textwidth]{figures/logo_UPPA}
\par\end{centering}
%
\vspace*{-2truemm}
%
\noindent \begin{centering}
\includegraphics[width=0.15\textwidth]{figures/logo_NVIDIA}\vspace*{2truemm}
\includegraphics[width=0.125\textwidth]{figures/logo_IUF}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Caltech}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_Harvard}\vspace*{2truemm}
\includegraphics[width=0.135\textwidth]{figures/logo_IPGP}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_ANR}\vspace*{2truemm}
\par\end{centering}
%
\vspace*{-2truemm}
%
\noindent \begin{centering}
\includegraphics[width=0.190\textwidth]{figures/logo_European_Union}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_GENCI}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_PRACE}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_CINES}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Oak_Ridge}\vspace*{2truemm}
\hspace*{3mm}\includegraphics[width=0.130\textwidth]{figures/logo_fondation_Del_Duca}
\par\end{centering}
%
\vspace*{-2truemm}
%
\noindent \begin{centering}
\includegraphics[width=0.112\textwidth]{figures/logo_University_of_Toronto}\vspace*{2truemm}
\includegraphics[width=0.119\textwidth]{figures/logo_INGV}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_Univ_Toulouse}\vspace*{2truemm}
\includegraphics[width=0.112\textwidth]{figures/logo_TOTAL}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Fairbanks}\vspace*{2truemm}
\includegraphics[width=0.140\textwidth]{figures/logo_Intel_Exascale_Labs}\vspace*{2truemm}
\includegraphics[width=0.130\textwidth]{figures/logo_Maison_Simulation}
\par\end{centering}
\end{figure}
